Are rankings of financial analysts useful to investors?

### 2015-03-12 doc/paper/paper-knitr-APS.Rnw
all tables per APS

\documentclass{article}
\usepackage{fancyhdr}
\usepackage{time}
\usepackage{authblk}
\usepackage{amsmath, amssymb}
\usepackage{caption}
\captionsetup[table]{textfont={large},labelfont={normalsize},labelsep=newline,justification=justified,singlelinecheck=true, skip=0pt}
\captionsetup[figure]{textfont={large},labelfont={normalsize},labelsep=newline,justification=justified,singlelinecheck=true, skip=0pt}
%\usepackage{fullpage}
%\usepackage{rotating}
%\usepackage{xcolor}
\usepackage[hyphens]{url}
\usepackage[colorlinks=true,urlcolor=blue,citecolor=black]{hyperref}
%\usepackage{breakurl}
\usepackage{times}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{array}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{multirow}
%\onehalfspacing
\doublespace
\usepackage[longnamesfirst]{natbib}
%\usepackage[natbibapa,longnamesfist]{apacite}

@@

Consistent with other studies on analysts' expected returns that work with price targets  \citep{bradshaw2002,brav2003,da2011}, we truncate the sample of $TP/P-1$ at the \Sexpr{ trunk.percent *100}\textsuperscript{th} percentile (values below \Sexpr{q.data[,min(trunk.view,na.rm=T)]}) and at the \Sexpr{(1-trunk.percent)*100}\textsuperscript{th} percentile (values above \Sexpr{ round(q.data[,max(trunk.view,na.rm=T)],3)}). This is done due to occurrence of the extreme values. Most of these extreme values are driven by misalignment errors found on I/B/E/S data\footnote{We found some differences between the  DataStream and I/B/E/S the databases. In some cases the stock-splits and the dividends were not properly adjusted.}. After trimming, the number of observations ($\mathrm{Stock} \times \mathrm{Broker} \times  \mathrm{Quarter}$) is reduced  from \Sexpr{ prettyNum(q.data[,.N], big.mark=' ')} to \Sexpr{ prettyNum(q.data[!is.na(trunk.view),.N],big.mark=' ')}.

@@

The \textit{TP} ranking strategy dominates also when we look at the risk-adjusted returns. The Sharpe Ratio is \Sexpr{ round(bl.results['TP',1,'ann.sr'],3)} against \Sexpr{ round(bl.results['CONS',1,'ann.sr'],3)}, \Sexpr{ round(bl.results['EPS',1,'ann.sr'],3)}, and \Sexpr{ round(bl.results['Market',1,'ann.sr'],3)}, respectively for the \textit{CONS}, the \textit{EPS}, and the \textit{Market} strategies. In addition, the \textit{TP} strategy dominates  the others if we consider the smaller trading periods (5 years). Table \ref{tab:substrategy} shows the Sharpe Ratio for six 5-year holding periods. The \textit{TP} strategy wins over the others in every period as expected.

@@

\subsection{Feasible strategies}
Panel C of table (\ref{tab:strategy}) shows the performance of the different smart strategies in the \naive{} information set. As it was the  case of the \tr{} information set, all the active strategies outperform the \textit{Market} (\Sexpr{bl.results['Market',2,1]}\%)  and show positive cumulative annualized returns of \Sexpr{bl.results['TP',2,1]}\%,  \Sexpr{bl.results['CONS',2,1]}\%, \Sexpr{bl.results['EPS',2,1]}\% respectively for the \textit{TP}, the \textit{CONS}, and the \textit{EPS} strategies. Similarly, the \textit{TP} strategy dominates when we consider the risk-adjusted returns. The Sharpe Ratio for this strategy is \Sexpr{ round(bl.results['TP',2,'ann.sr'],3)} which is higher than that Sharpe Ratios of the \textit{CONS} and  the \textit{EPS} strategies  (\Sexpr{ round(bl.results['CONS',2,'ann.sr'],3)} and \Sexpr{ round(bl.results['EPS',2,'ann.sr'],3)} respectively). The results in panel B of table \ref{tab:substrategy} show as well that this strategy outperform the others for all of 5 trading sub-periods.

@@

options(xtable.comment = FALSE)
#cat(rep('&',ncol(results.final)),'\\\\')
print(xtable(brok.full.stat.pt,display=c('s','d','f','f','f','d','f')),only.contents=T,include.colnames=FALSE,include.rownames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(11),command=c('\\midrule \n')))
@
\end{tabularx}

\begin{tabularx}{\linewidth}{r*{6}{Y}}
\midrule
\multicolumn{6}{c}{\textbf{Panel B: EPS}} \\
\midrule
<<desc-eps,echo=F,results='asis'>>=
print(xtable(brok.full.stat.eps,display=c('s','d','f','f','f','d','f')),only.contents=T,include.colnames=FALSE,include.rownames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(11),command=c('\\midrule \n')))
@
\bottomrule
\end{tabularx}
\end{table}

@@

\begin{table}[hp]
  \caption{Trading strategies performance: entire period}
  \label{tab:strategy}
  \ This table shows the performance statistics of the different trading strategies. Panel A presents the results for the passive strategy. Panels B,C, and D show the results for the perfect foresight scenario (\tr{}), and, respectively, the scenarios for which we use the most recent  (\naive{}); and  all ranking history of analysts (\default{}) to weight the TP/EPS estimates . Within each panel, we show the strategy results of three views regarding expected return: \textit{CONS} uses the median of the analysts estimates; \textit{TP} is based upon TP accuracy ranking; and \textit{EPS} is based upon  EPS accuracy ranking. The trading period goes from \Sexpr{gsub('[[:space:]]','',final.bl[,head(Quarters,1)])} until \Sexpr{gsub('[[:space:]]','',final.bl[,tail(Quarters,1)])}.

@@

\begin{table}[hp]
  \caption{Trading strategies performance: sub-periods}
  \label{tab:substrategy}
  \ This table presents the Sharpe ratio of each of the trading strategies: the passive (\textit{Market}) and the active (consensus and smart estimates) calculated for different holding periods. Panel A represents the perfect foresight information set; panels B and C show, respectively, the results of the strategies using the most recent and all history analysts' performance. 
\begin{tabularx}{\linewidth}{r*{5}{Y}}
\toprule
  %\multicolumn{5}{l}{\textbf{Panel A: Market}} \\
<<sr-true,echo=F,results='asis'>>=

#results.final <- bl.results['Market',1,]
cat(paste(c('Period','\\textit{Market}','\\textit{CONS}','\\textit{TP}','\\textit{EPS}'), collapse = "&"),'\\\\')
#cat('\\multicolumn{5}{l}{\\textbf{Panel A: Market}} \n')
print(xtable(periods.array[,c(4,1,2,3),1,'yes','sr'],display=c('s','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0),command=c('\\multicolumn{5}{l}{\\textbf{Panel A: \\tr{}}} \\\\\n')))
@
\midrule
\end{tabularx}

\begin{tabularx}{\linewidth}{r*{5}{Y}}
<<sr-naive,echo=F,results='asis'>>=
print(xtable(periods.array[,c(4,1,2,3),2,'yes','sr'],display=c('s','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0),command=c('\\multicolumn{5}{l}{\\textbf{Panel B: \\naive{}}} \\\\\n')))
@
\midrule
\end{tabularx}

\begin{tabularx}{\linewidth}{r*{5}{Y}}
<<sr-default,echo=F,results='asis'>>=
print(xtable(periods.array[,c(4,1,2,3),3,'yes','sr'],display=c('s','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0),command=c('\\multicolumn{5}{l}{\\textbf{Panel C: \\default{}}} \\\\\n')))
@
\bottomrule
\end{tabularx}
\end{table}

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=\linewidth]{figure/example-fig-1}
\end{center}
\caption{Daily stock price Amazon and brokers target prices}
\label{fig:example}
\ Target price and actual prices for Amazon  the second quarter of 1999.
\end{figure}

>>>>

\documentclass{article}
\usepackage{fancyhdr}
\usepackage{time}
\usepackage{authblk}
\usepackage{amsmath, amssymb}
\usepackage{caption}
\captionsetup[table]{textfont={large},labelfont={normalsize},labelsep=newline,justification=justified,singlelinecheck=true, skip=0pt}
\captionsetup[figure]{textfont={large},labelfont={normalsize},labelsep=newline,justification=justified,singlelinecheck=true, skip=0pt}
%\usepackage{fullpage}
%\usepackage{rotating}
%\usepackage{xcolor}
\usepackage[hyphens]{url}
\usepackage[colorlinks=true,urlcolor=blue,citecolor=black]{hyperref}
%\usepackage{breakurl}
\usepackage{times}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{array}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{adjustbox}
%\onehalfspacing
\doublespace
\usepackage[longnamesfirst]{natbib}
%\usepackage[natbibapa,longnamesfist]{apacite}

@@

Consistent with other studies on analysts' expected returns that work with price targets  \citep{bradshaw2002,brav2003,da2011}, we truncate the sample of $TP/P-1$ at the \Sexpr{ trunk.percent *100}\textsuperscript{th} percentile (values below \Sexpr{q.data[,min(trunk.view,na.rm=T)]}) and at the \Sexpr{(1-trunk.percent)*100}\textsuperscript{th} percentile (values above \Sexpr{ q.data[,max(trunk.view,na.rm=T)]}). This is done due to occurrence of the extreme values. Most of these extreme values are driven by misalignment errors found on I/B/E/S data\footnote{We found some differences between the  DataStream and I/B/E/S the databases. In some cases the stock-splits and the dividends were not properly adjusted.}. After trimming, the number of observations ($\mathrm{Stock} \times \mathrm{Broker} \times  \mathrm{Quarter}$) is reduced  from \Sexpr{ prettyNum(q.data[,.N], big.mark=' ')} to \Sexpr{ prettyNum(q.data[!is.na(trunk.view),.N],big.mark=' ')}.

@@

The \textit{TP} ranking strategy dominates also when we look at the risk-adjusted returns. The Sharpe Ratio is \Sexpr{ bl.results['TP',1,'ann.sr']} against \Sexpr{ bl.results['CONS',1,'ann.sr']}, \Sexpr{ bl.results['EPS',1,'ann.sr']}, and \Sexpr{ bl.results['Market',1,'ann.sr']}, respectively for the \textit{CONS}, the \textit{EPS}, and the \textit{Market} strategies. In addition, the \textit{TP} strategy dominates  the others if we consider the smaller trading periods (5 years). Table \ref{tab:substrategy} shows the Sharpe Ratio for six 5-year holding periods. The \textit{TP} strategy wins over the others in every period as expected.

@@

\subsection{Feasible strategies}
Panel C of table (\ref{tab:strategy}) shows the performance of the different smart strategies in the \naive{} information set. As it was the  case of the \tr{} information set, all the active strategies outperform the \textit{Market} (\Sexpr{bl.results['Market',2,1]}\%)  and show positive cumulative annualized returns of \Sexpr{bl.results['TP',2,1]}\%,  \Sexpr{bl.results['CONS',2,1]}\%, \Sexpr{bl.results['EPS',2,1]}\% respectively for the \textit{TP}, the \textit{CONS}, and the \textit{EPS} strategies. Similarly, the \textit{TP} strategy dominates when we consider the risk-adjusted returns. The Sharpe Ratio for this strategy is \Sexpr{ bl.results['TP',2,'ann.sr']} which is higher than that Sharpe Ratios of the \textit{CONS} and  the \textit{EPS} strategies  (\Sexpr{ bl.results['CONS',2,'ann.sr']} and \Sexpr{bl.results['EPS',2,'ann.sr']} respectively). The results in panel B of table \ref{tab:substrategy} show as well that this strategy outperform the others for all of 5 trading sub-periods.

@@

options(xtable.comment = FALSE)
#cat(rep('&',ncol(results.final)),'\\\\')
print(xtable(brok.full.stat.pt,display=c('s','f','d','f','f','d','f'),digits=3),only.contents=T,include.colnames=FALSE,include.rownames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(11),command=c('\\midrule \n')))
@
\end{tabularx}

\begin{tabularx}{\linewidth}{r*{6}{Y}}
\midrule
\multicolumn{6}{c}{\textbf{Panel B: EPS}} \\
\midrule
<<desc-eps,echo=F,results='asis'>>=
print(xtable(brok.full.stat.eps,display=c('s','d','d','f','f','d','f'),digits=3),only.contents=T,include.colnames=FALSE,include.rownames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(11),command=c('\\midrule \n')))
@
\bottomrule
\end{tabularx}
\end{table}

@@

\begin{table}[hp]
  \caption{Trading strategies performance: entire period}
  \label{tab:strategy}
  \ This table shows the performance statistics of the different trading strategies. Panel A presents the results for the passive strategy. Panels B,C, and D show the results for the perfect foresight scenario (\tr{}), and, respectively, the scenarios for which we use the most recent  (\naive{}) and  all ranking history of analysts (\default{}) to weight the TP/EPS estimates . Within each panel, we show the strategy results of three views regarding expected return: \textit{CONS} uses the median of the analysts estimates; \textit{TP} is based upon TP accuracy ranking; and \textit{EPS} is based upon  EPS accuracy ranking. The trading period goes from \Sexpr{gsub('[[:space:]]','',final.bl[,head(Quarters,1)])} until \Sexpr{gsub('[[:space:]]','',final.bl[,tail(Quarters,1)])}.

@@

\begin{table}[hp]
  \caption{Trading strategies performance: sub-periods}
  \label{tab:substrategy}
  \ This table presents the annualized return (in \%) and the Sharpe ratio of each of the trading strategies: the passive (\textit{Market}) and the active (consensus and smart estimates) calculated for different holding periods. Panel A represents the perfect foresight information set; panels B and C show, respectively, the results of the strategies using the most recent and all history analysts' performance.

\resizebox{\textwidth}{!}{%
%\begin{tabularx}{\linewidth}{r*{9}{Y}}
\begin{tabular}{rrrrrrrrr}
\toprule
Period&\multicolumn{2}{c}{\textit{Market}}&\multicolumn{2}{c}{\textit{CONS}}&\multicolumn{2}{c}{\textit{TP}}&\multicolumn{2}{c}{\textit{EPS}} \\

& Ann.ret&SR& Ann.ret&SR& Ann.ret&SR& Ann.ret&SR\\

<<sr-true,echo=F,results='asis'>>=
periods.array[,,,,1] <- periods.array[,,,,1]*100
#results.final <- bl.results['Market',1,]
#cat(paste(c('Period','\\textit{Market}','\\textit{CONS}','\\textit{TP}','\\textit{EPS}'), collapse = "&"),'\\\\')
#cat('\\multicolumn{5}{l}{\\textbf{Panel A: Market}} \n')
#print(xtable(periods.array[,c(4,1,2,3),1,'yes','sr'],display=c('s','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0),command=c('\\multicolumn{5}{l}{\\textbf{Panel A: \\tr{}}} \\\\\n')))

print(xtable(acast(melt(periods.array[,c(4,1,2,3),1,'yes',c(1,4)]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,6),command=c('\\multicolumn{9}{l}{\\textbf{Panel A: \\tr{}}} \\\\\n', '\\midrule \n')))

@
\midrule
\end{tabular}}

\resizebox{\textwidth}{!}{%
\begin{tabular}{rrrrrrrrr}
%\begin{tabularx}{\linewidth}{r*{9}{Y}}
<<sr-naive,echo=F,results='asis'>>=
#print(xtable(periods.array[,c(4,1,2,3),2,'yes','sr'],display=c('s','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0),command=c('\\multicolumn{5}{l}{\\textbf{Panel B: \\naive{}}} \\\\\n')))

print(xtable(acast(melt(periods.array[,c(4,1,2,3),2,'yes',c(1,4)]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,6),command=c('\\multicolumn{9}{l}{\\textbf{Panel B: \\naive{}}} \\\\\n', '\\midrule \n')))

@
\midrule
\end{tabular}}
\resizebox{\textwidth}{!}{%
\begin{tabular}{rrrrrrrrr}
%\begin{tabularx}{\linewidth}{r*{9}{Y}}
<<sr-default,echo=F,results='asis'>>=
#print(xtable(periods.array[,c(4,1,2,3),3,'yes','sr'],display=c('s','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0),command=c('\\multicolumn{5}{l}{\\textbf{Panel C: \\default{}}} \\\\\n')))

print(xtable(acast(melt(periods.array[,c(4,1,2,3),3,'yes',c(1,4)]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,6),command=c('\\multicolumn{5}{l}{\\textbf{Panel C: \\default{}}} \\\\\n','\\midrule \n')))
@
\bottomrule
\end{tabular}}
\end{table}

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=\linewidth]{figure/example-fig-1}
\end{center}
\caption{Amazon daily stock price and brokers target prices}
\label{fig:example}
\ Target price and actual prices for Amazon  the second quarter of 1999.
\end{figure}
